---
title: "More Fragments"
subtitle: "Additional fragment animations for RevealJS"
format: revealjs
filters:
  - ../_extensions/more-fragments/more-fragments.lua
---

## What is this?

This extension provides additional fragment animations for RevealJS presentations.

::: {.fragment .bounceIn}
Animations are powered by [Animate.css](https://animate.style/)
:::

::: {.fragment .backInUp}
All animations work **forwards** and **backwards**!
:::

## Basic Usage

Use any animation class with `.fragment`:

```markdown
::: {.fragment .bounceIn}
This text bounces in!
:::
```

::: {.fragment .bounceIn}
This text bounces in!
:::

## Inline Animations

Animations work on inline elements too:

```markdown
The [quick]{.fragment .backInUp} [brown]{.fragment .tada}
[fox]{.fragment .bounceIn} jumps.
```

The [quick]{.fragment .backInUp} [brown]{.fragment .tada} [fox]{.fragment .bounceIn} jumps over the lazy dog.

## Attention Seekers

These animations keep elements visible and animate when triggered:

:::: {.columns}
::: {.column width="50%"}
::: {.fragment .bounce}
bounce
:::

::: {.fragment .pulse}
pulse
:::

::: {.fragment .tada}
tada
:::
:::

::: {.column width="50%"}
::: {.fragment .wobble}
wobble
:::

::: {.fragment .heartBeat}
heartBeat
:::

::: {.fragment .jello}
jello
:::
:::
::::

## Entrance Animations

Elements appear with directional movement:

:::: {.columns}
::: {.column width="50%"}
::: {.fragment .backInUpDown}
backInUpDown
:::

::: {.fragment .bounceInLeft}
bounceInLeft
:::

::: {.fragment .zoomIn}
zoomIn
:::
:::

::: {.column width="50%"}
::: {.fragment .slideInRight}
slideInRight
:::

::: {.fragment .rotateIn}
rotateIn
:::

::: {.fragment .jackInTheBox}
jackInTheBox
:::
:::
::::

## Exit Animations

Elements disappear with directional movement:

:::: {.columns}
::: {.column width="50%"}
::: {.fragment .fadeOut}
fadeOut
:::

::: {.fragment .bounceOut}
bounceOut
:::

::: {.fragment .zoomOut}
zoomOut
:::
:::

::: {.column width="50%"}
::: {.fragment .slideOutLeft}
slideOutLeft
:::

::: {.fragment .rotateOut}
rotateOut
:::

::: {.fragment .hinge}
hinge
:::
:::
::::

## Speed Utilities

Control animation speed with utility classes:

::: {.fragment .bounceIn .slower}
slower (3s)
:::

::: {.fragment .bounceIn .slow}
slow (2s)
:::

::: {.fragment .bounceIn}
default (1s)
:::

::: {.fragment .bounceIn .fast}
fast (800ms)
:::

::: {.fragment .bounceIn .faster}
faster (500ms)
:::

## Reversible Behavior

All animations reverse naturally when navigating backwards.

::: {.fragment .backInUpDown}
`backInUpDown` enters from top...
:::

::: {.fragment .backInUp}
...and exits back to top with `backOutUp`
:::

::: {.fragment .slideInLeft}
Try pressing the **left arrow** to see animations reverse!
:::

## Header Animations {.fragment .bounceIn}

Headers can now be animated as fragments too!

::: {.fragment .fadeIn}
Use the same syntax: `## Title {.fragment .bounceIn}`
:::

## Fast Header {.fragment .zoomIn .faster}

Speed utilities work on headers:

::: {.fragment .backInUp}
`## Fast Header {.fragment .zoomIn .faster}`
:::

## Whole Slide Animation {.fragment-slide .bounceIn}

This entire slide animates as a single fragment.

Both the header and content animate together.

Use `.fragment-slide` instead of `.fragment`.

## Animated Plots

Wrap code chunks in fragment divs to animate plots:

::: {.fragment .zoomIn}
```{r}
#| echo: false
#| fig-width: 6
#| fig-height: 3
plot(pressure, main = "Pressure Data")
```
:::

::: {.fragment .bounceIn}
```{r}
#| echo: false
#| fig-width: 6
#| fig-height: 3
hist(mtcars$mpg, main = "MPG Distribution", col = "steelblue")
```
:::

## Sequential Plot Animations

:::: {.columns}
::: {.column width="50%"}
::: {.fragment .fadeInLeft}
```{r}
#| echo: false
#| fig-width: 4
#| fig-height: 4
plot(mtcars$mpg, mtcars$hp, pch = 19, col = "darkred",
     xlab = "MPG", ylab = "Horsepower")
```
:::
:::

::: {.column width="50%"}
::: {.fragment .fadeInRight}
```{r}
#| echo: false
#| fig-width: 4
#| fig-height: 4
plot(mtcars$wt, mtcars$qsec, pch = 19, col = "darkblue",
     xlab = "Weight", ylab = "Quarter Mile Time")
```
:::
:::
::::

## Whole Slide with Plot {.fragment-slide .fadeIn}

```{r}
#| echo: false
#| fig-width: 8
#| fig-height: 4
#| fig-align: center
barplot(table(mtcars$cyl), col = c("coral", "steelblue", "seagreen"),
        main = "Cars by Cylinder Count", xlab = "Cylinders", ylab = "Count")
```

The title and plot animate together as one fragment.

## Letter-by-Letter Animations

Text can animate letter by letter with a single fragment step:

[Hello World]{.fragment-letters .bounceIn}

[Welcome to RevealJS]{.fragment-letters .fadeIn}

## Letter Animation Speeds

Control the stagger delay between letters:

[Fast typing]{.fragment-letters .fadeIn .letter-fast}

[Default speed]{.fragment-letters .fadeIn}

[Slow reveal]{.fragment-letters .zoomIn .letter-slow}

## Different Letter Animations

Various animation styles work with letters:

[Bounce effect]{.fragment-letters .bounceIn}

[Zoom from small]{.fragment-letters .zoomIn}

[Slide from left]{.fragment-letters .slideInLeft}

[Rotate in]{.fragment-letters .rotateIn}

## Letters with Speed Utilities

Combine letter animations with animation speed:

[Quick bounce]{.fragment-letters .bounceIn .faster .letter-fast}

[Slow zoom]{.fragment-letters .zoomIn .slow .letter-slower}

# Header animation {.fragment-letters .bounceIn}

Letter-by-letter works on headers too!

## Learn More

::: {.fragment .backInUp}
See the [full animation gallery](animations.html) for all available animations.
:::

::: {.fragment .backInUp}
Visit [Animate.css](https://animate.style/) for animation documentation.
:::
